Nesta attacks study

### 2021-08-25 paperDraft/paperDraft.Rmd
theoretical intro improved

# Introduction
Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys \todo{refs}, it remains a common hindrance for people engaging with social media in their everyday lives. The problem got exacerbated in the midst of the COVID19 pandemic \todo{is it less coloquial now?}, during which a majority of our social life moved to cyberspace. During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content @grant_2021, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.} According to a report conducted by company L1ght [@noauthor_l1ght_2020], hate speech directed towards China and the Chinese went up by 900% on Twitter. Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord \footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.

@@

\todo{This deserves a developed paragraph with examples}Lack of generalisability of the models---an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well [@yin2021towards; @swamy2019studying; @rosa2019automatic]. As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility. This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public. Specifically, @@lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike. First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second\todo{give an example}. Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect)\todo{give an example}. Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon\todo{Give an example}. Last but not least---misuse of language\todo{Give an example}. This includes suggestive definitions without proper explanation of what they mean in the context (e.g. inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g. consciousness).

@@

At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms. On Facebook, there are more than 3B comments and likes daily [@noauthor_facebook:_2012], 500M tweets are sent daily on Twitter [@noauthor_10_2021], and over 2B comments made by users of Reddit in 2020 [@noauthor_reddit_nodate] which is almost 3M comments made daily. With this amount of content, it's either impossible or extremely costly to scale the moderation workforce. One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being. Being submersed in the cyber-Augean stables takes a toll on many---as examined by @roberts2014behind & @roberts2016commercial. Workers hired for such tasks are often low-status and low-wage, isolated and asked to keep what they've seen in secret under restrictive NDAs. This in turn makes the research in the area extremely difficult, since moderators are not allowed to talk about their work conditions or any other related subject. Those who decided to break the NDA are risking a penalty. 
Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases. This can lead to serious psychological damage, such as depression, or PTSD [@roberts2014behind]. Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job [@newton_facebook_2020].
Taking into consideration that Facebook employs 15K moderators [@koetsier_report] and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.

@@

# Collective Intelligence Approach to Counter-speech

>>>>

# Introduction
Although much effort has been made in order to tackle the problem of verbal aggression and harassment online, looking at various reports and surveys [@sorrentino2019epidemiology; @vogels_state_2021; @Zachary_hate], it remains a common hindrance for people engaging with social media in their everyday lives. The problem got exacerbated in the midst of the COVID19 pandemic\todo{is it less coloquial now?}, during which a majority of our social life moved to cyberspace. During this shift, there was an increase in cyberbullying attitudes and perpetration (@barlett2021comparing), 90% increase in public reports of illegal online content @grant_2021, including 114% increase in non-consensual sharing of intimate images, 30% increase in cyberbullying, as well as 40% of increase in adults reporting online harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.} According to a report conducted by company L1ght [@noauthor_l1ght_2020], hate speech directed towards China and the Chinese went up by 900% on Twitter. Gaming platforms were in the spotlight as well, with a 40% increase in toxicity on Discord \footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.

@@

\todo{This deserves a developed paragraph with examples}Lack of generalisability of the models---an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well [@yin2021towards; @swamy2019studying; @rosa2019automatic].

As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility. This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public. Specifically, @lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike. First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second. For instance, in a paper from 2017 [@steinhardt2017certified], Jacob Steinhardt, the author of @lipton2019troubling, admitted to stating that “the high dimensionality and abundance of irrelevant features... give the attacker more room to construct attacks” - although no experiments were conducted to measure what is the effect of dimensionality of the neural network on its attackability. Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect). As was shown by Gabor Melis, Chris Dyer, and Phil Blunsom, some improvements in language modeling which originally were ascribed to complex innovations in the architecture of the network, stemed from hyperparameter tuning [@melis2017state]. As mentioned by @lipton2019troubling, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon. Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang [@steinhardt2015learning] with irrelevant theorem to amplify the empirical results. They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm---the main subject of a paper. 
Last but not least---misuse of language\todo{Give an example}. This includes suggestive definitions without proper explanation of what they mean in the context (e.g. inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g. consciousness)

@@

At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms. On Facebook, there are more than 3B comments and likes daily [@noauthor_facebook:_2012], 500M tweets are sent daily on Twitter [@noauthor_10_2021], and over 2B comments made by users of Reddit in 2020 [@noauthor_reddit_nodate] which is almost 3M comments made daily. With this amount of content, it's either impossible or extremely costly to scale the moderation workforce. One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being. Being submersed in the cyber-Augean stables takes a toll on many---as examined by @roberts2014behind & @roberts2016commercial. Workers hired for such tasks are often low-status and low-wage, isolated and asked to keep what they've seen in secret under restrictive NDAs. This in turn makes the research in the area extremely difficult, since moderators are not allowed to talk about their work conditions or any other related subject. Those who decided to break the NDA are risking a penalty. 
Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases. This can lead to serious psychological damage, such as depression, or PTSD [@roberts2014behind]. Although there are certain initiatives being developed or introduced to reduce the emotional impact of the moderation, like stylistic alterations to a content (applying grayscale or blurring to images) [@karunakaran2019testing], workplace wellness programs, clinical support, or psychological training [@steiger2021psychological], none of the methods can eliminate the psychological distress completely. Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job [@newton_facebook_2020]. Also as described by @parks2019dirty, the work is often performed under time pressure, reviewing 25K pieces of content per day. Spending on average three to five seconds on each image reported for moderation might not lead to the most thoughtful decisions and as shown @stepanikova2012racial, high time pressure can amplify human biases.
Taking into consideration that Facebook employs 15K moderators [@koetsier_report] and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.

@@

# Collective Intelligence Approach to Counter-speech
Traditionally collective intelligence has been defined as "a group or a team’s combined capacity and capability to perform a wide variety of tasks and solve diverse problems" [@noauthor_collective_nodate]. In our paper and in the theoretical underpinnings of the experiment itself, we will be relying on a collective intelligence scope proposed by Nesta, an innovation foundation (https://www.nesta.org.uk), which focuses on a collaboration between human and machine intelligence to develop innovative solutions to social challenges. (Gdzieś stopka(?): Samurai Labs has been one of the 15 recipients of the second round of collective intelligence grants awarded by Nesta: https://www.nesta.org.uk/project-updates/second-round-collective-intelligence-grants/)

The main objective of the experiment was to test whether the level of verbal aggression (personal attacks) of a group of users' regularly attacking others on Reddit can be significantly decreased by community-driven, counter-speech interventions conducted by volunteers in partnership with Artificial Intelligence. Instead of using negative motivation system, the assumption was to test a positive one - convincing vrbally violent users to refrain from using cyberviolence based on peer-pressure regulation and experiential learning of a positive set of norms and empathy. Algorithms developed for the detection of personal attacks were used to monitor the activity of experimental groups and notify volunteers about all attacks generated by its' members. Volunteers, after receiving a notification on Slack (perhaps say more about those processes and infrastructure), could then react with the proper intervention. Such an approach served as a distributed bottom-up voluntary model of moderation based on collective intelligence - utilizing human + machine intelligence.

In the end, what we were able to compare was the following: the effectiveness of the existing Reddit moderation system (predominantly grounded in a punitive authoritarian paradigm) versus the existing moderation system combined with collective intelligence - Artificial Intelligence supported with a crowd of volunteers - who introduced the element of  positive peer-pressure.

### 2021-08-25 paperDraft/paperDraft.tex
theoretical intro improved

Although much effort has been made in order to tackle the problem of
verbal aggression and harassment online, looking at various reports and
surveys \todo{refs}, it remains a common hindrance for people engaging
with social media in their everyday lives. The problem got exacerbated
in the midst of the COVID19 pandemic \todo{is it less coloquial now?},
during which a majority of our social life moved to cyberspace. During
this shift, there was an increase in cyberbullying attitudes and
perpetration (Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase
in public reports of illegal online content Grant (2021), including
114\% increase in non-consensual sharing of intimate images, 30\%
increase in cyberbullying, as well as 40\% of increase in adults
reporting online
harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
According to a report conducted by company L1ght (L1ght, 2020), hate
speech directed towards China and the Chinese went up by 900\% on
Twitter. Gaming platforms were in the spotlight as well, with a 40\%
increase in toxicity on Discord
\footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.

@@

\todo{This deserves a developed paragraph with examples}Lack of
generalisability of the models---an ability to perform well on datasets
coming from sources other than the one used for training is a serious
shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
2019; Yin \& Zubiaga, 2021). As shown by Wu, Ribeiro, Heer, \& Weld
(2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
(2020) in practice, the development of such models often lacks thorough
error analysis and legitimate experimental methodology, which can result
in non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, @Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the
second\todo{give an example}. Second, the inability of successful
identification of the sources of performance improvement (whether it was
problem formulation, optimization of the heuristics, data-preprocessing,
hyperparameter tuning, or perhaps yet another
aspect)\todo{give an example}. Third, ``mathiness''---the use of obscure
language and often covering weak argumentation with the alluring but
often apparent depth of technical jargon\todo{Give an example}. Last but
not least---misuse of language\todo{Give an example}. This includes
suggestive definitions without proper explanation of what they mean in
the context (e.g.~inflating good performance in simple NLP tasks to
human-level understanding), overloading the papers with technical
terminology, or suitcase words (words that can encompass a variety of
meanings, e.g.~consciousness).

@@

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
({``Facebook,''} 2012), 500M tweets are sent daily on Twitter (\emph{10
{Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in 2021
{[}{Infographic}{]}}, 2021), and over 2B comments made by users of
Reddit in 2020 ({``Reddit in 2020,''} 2020) which is almost 3M comments
made daily. With this amount of content, it's either impossible or
extremely costly to scale the moderation workforce. One can also have
doubts about the ethical aspects of hiring workers who are often unaware
of how this kind of task will affect their well-being. Being submersed
in the cyber-Augean stables takes a toll on many---as examined by
Roberts (2014) \& Roberts (2016). Workers hired for such tasks are often
low-status and low-wage, isolated and asked to keep what they've seen in
secret under restrictive NDAs. This in turn makes the research in the
area extremely difficult, since moderators are not allowed to talk about
their work conditions or any other related subject. Those who decided to
break the NDA are risking a penalty. Screening through the reported
user-generated content is connected with exposure to violent and deeply
disturbing materials, with child pornography, murders, or suicides as
examples of the most extreme cases. This can lead to serious
psychological damage, such as depression, or PTSD (Roberts, 2014). Some
of the employees filed a lawsuit against Facebook and as a result, the
company agreed to pay \$52M in compensation for mental health issues
developed during the job (Newton, 2020). Taking into consideration that
Facebook employs 15K moderators (Koetsier, 2020) and most likely more
are needed to keep up with the growing amount of content, with the
parallel considerations about the negative effects of content moderation
on mental health, a collaboration between humans and machines in this
area seems inevitable.

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Although much effort has been made in order to tackle the problem of
verbal aggression and harassment online, looking at various reports and
surveys (Laub, 2019; Sorrentino, Baldry, Farrington, \& Blaya, 2019;
Vogels, 2021), it remains a common hindrance for people engaging with
social media in their everyday lives. The problem got exacerbated in the
midst of the COVID19 pandemic\todo{is it less coloquial now?}, during
which a majority of our social life moved to cyberspace. During this
shift, there was an increase in cyberbullying attitudes and perpetration
(Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase in public
reports of illegal online content Grant (2021), including 114\% increase
in non-consensual sharing of intimate images, 30\% increase in
cyberbullying, as well as 40\% of increase in adults reporting online
harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
According to a report conducted by company L1ght (L1ght, 2020), hate
speech directed towards China and the Chinese went up by 900\% on
Twitter. Gaming platforms were in the spotlight as well, with a 40\%
increase in toxicity on Discord
\footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.

@@

\todo{This deserves a developed paragraph with examples}Lack of
generalisability of the models---an ability to perform well on datasets
coming from sources other than the one used for training is a serious
shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
2019; Yin \& Zubiaga, 2021).

As shown by Wu, Ribeiro, Heer, \& Weld (2019), Lipton \& Steinhardt
(2019), and Musgrave, Belongie, \& Lim (2020) in practice, the
development of such models often lacks thorough error analysis and
legitimate experimental methodology, which can result in
non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the second. For
instance, in a paper from 2017 (Steinhardt, Koh, \& Liang, 2017), Jacob
Steinhardt, the author of Lipton \& Steinhardt (2019), admitted to
stating that ``the high dimensionality and abundance of irrelevant
features\ldots{} give the attacker more room to construct attacks'' -
although no experiments were conducted to measure what is the effect of
dimensionality of the neural network on its attackability. Second, the
inability of successful identification of the sources of performance
improvement (whether it was problem formulation, optimization of the
heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
another aspect). As was shown by Gabor Melis, Chris Dyer, and Phil
Blunsom, some improvements in language modeling which originally were
ascribed to complex innovations in the architecture of the network,
stemed from hyperparameter tuning (Melis, Dyer, \& Blunsom, 2017). As
mentioned by Lipton \& Steinhardt (2019), there is a tremendous value
coming from the thorough understanding of a particular method, and a
variety of techniques are vital in the process (like ablation,
robustness checks, qualitative error analysis) for the benefit of the
whole community. Third, ``mathiness''---the use of obscure language and
often covering weak argumentation with the alluring but often apparent
depth of technical jargon. Again Jacob Steinhardt admitted infusing his
2015 paper co-authored with Percy Liang (Steinhardt \& Liang, 2015) with
irrelevant theorem to amplify the empirical results. They discussed
``staged strong Doeblin chains'' which actually had limited pertinence
to the learning algorithm---the main subject of a paper. Last but not
least---misuse of language\todo{Give an example}. This includes
suggestive definitions without proper explanation of what they mean in
the context (e.g.~inflating good performance in simple NLP tasks to
human-level understanding), overloading the papers with technical
terminology, or suitcase words (words that can encompass a variety of
meanings, e.g.~consciousness)

@@

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
({``Facebook,''} 2012), 500M tweets are sent daily on Twitter (\emph{10
{Twitter} {Statistics} {Every} {Marketer} {Should} {Know} in 2021
{[}{Infographic}{]}}, 2021), and over 2B comments made by users of
Reddit in 2020 ({``Reddit in 2020,''} 2020) which is almost 3M comments
made daily. With this amount of content, it's either impossible or
extremely costly to scale the moderation workforce. One can also have
doubts about the ethical aspects of hiring workers who are often unaware
of how this kind of task will affect their well-being. Being submersed
in the cyber-Augean stables takes a toll on many---as examined by
Roberts (2014) \& Roberts (2016). Workers hired for such tasks are often
low-status and low-wage, isolated and asked to keep what they've seen in
secret under restrictive NDAs. This in turn makes the research in the
area extremely difficult, since moderators are not allowed to talk about
their work conditions or any other related subject. Those who decided to
break the NDA are risking a penalty. Screening through the reported
user-generated content is connected with exposure to violent and deeply
disturbing materials, with child pornography, murders, or suicides as
examples of the most extreme cases. This can lead to serious
psychological damage, such as depression, or PTSD (Roberts, 2014).
Although there are certain initiatives being developed or introduced to
reduce the emotional impact of the moderation, like stylistic
alterations to a content (applying grayscale or blurring to images)
(Karunakaran \& Ramakrishan, 2019), workplace wellness programs,
clinical support, or psychological training (Steiger, Bharucha,
Venkatagiri, Riedl, \& Lease, 2021), none of the methods can eliminate
the psychological distress completely. Some of the employees filed a
lawsuit against Facebook and as a result, the company agreed to pay
\$52M in compensation for mental health issues developed during the job
(Newton, 2020). Also as described by Parks (2019), the work is often
performed under time pressure, reviewing 25K pieces of content per day.
Spending on average three to five seconds on each image reported for
moderation might not lead to the most thoughtful decisions and as shown
Stepanikova (2012), high time pressure can amplify human biases. Taking
into consideration that Facebook employs 15K moderators (Koetsier, 2020)
and most likely more are needed to keep up with the growing amount of
content, with the parallel considerations about the negative effects of
content moderation on mental health, a collaboration between humans and
machines in this area seems inevitable.

@@

Traditionally collective intelligence has been defined as ``a group or a
team's combined capacity and capability to perform a wide variety of
tasks and solve diverse problems'' ({``Collective {Intelligence},''}
n.d.). In our paper and in the theoretical underpinnings of the
experiment itself, we will be relying on a collective intelligence scope
proposed by Nesta, an innovation foundation
(\url{https://www.nesta.org.uk}), which focuses on a collaboration
between human and machine intelligence to develop innovative solutions
to social challenges. (Gdzieś stopka(?): Samurai Labs has been one of
the 15 recipients of the second round of collective intelligence grants
awarded by Nesta:
\url{https://www.nesta.org.uk/project-updates/second-round-collective-intelligence-grants/})

The main objective of the experiment was to test whether the level of
verbal aggression (personal attacks) of a group of users' regularly
attacking others on Reddit can be significantly decreased by
community-driven, counter-speech interventions conducted by volunteers
in partnership with Artificial Intelligence. Instead of using negative
motivation system, the assumption was to test a positive one -
convincing vrbally violent users to refrain from using cyberviolence
based on peer-pressure regulation and experiential learning of a
positive set of norms and empathy. Algorithms developed for the
detection of personal attacks were used to monitor the activity of
experimental groups and notify volunteers about all attacks generated by
its' members. Volunteers, after receiving a notification on Slack
(perhaps say more about those processes and infrastructure), could then
react with the proper intervention. Such an approach served as a
distributed bottom-up voluntary model of moderation based on collective
intelligence - utilizing human + machine intelligence.

In the end, what we were able to compare was the following: the
effectiveness of the existing Reddit moderation system (predominantly
grounded in a punitive authoritarian paradigm) versus the existing
moderation system combined with collective intelligence - Artificial
Intelligence supported with a crowd of volunteers - who introduced the
element of positive peer-pressure.

@@

\leavevmode\hypertarget{ref-noauthor_collective_nodate}{}%
Collective {Intelligence}. (n.d.). Retrieved from
\url{https://www.oxford-review.com/oxford-review-encyclopaedia-terms/collective-intelligence/}

@@

\leavevmode\hypertarget{ref-karunakaran2019testing}{}%
Karunakaran, S., \& Ramakrishan, R. (2019). Testing stylistic
interventions to reduce emotional impact of content moderation workers.
\emph{Proceedings of the AAAI Conference on Human Computation and
Crowdsourcing}, \emph{7}, 50--58.

@@

\leavevmode\hypertarget{ref-Zachary_hate}{}%
Laub, Z. (2019). Hate {Speech} on {Social} {Media}: {Global}
{Comparisons}. Retrieved from
\url{https://www.cfr.org/backgrounder/hate-speech-social-media-global-comparisons}

@@

\leavevmode\hypertarget{ref-melis2017state}{}%
Melis, G., Dyer, C., \& Blunsom, P. (2017). On the state of the art of
evaluation in neural language models. \emph{arXiv Preprint
arXiv:1707.05589}.

@@

\leavevmode\hypertarget{ref-parks2019dirty}{}%
Parks, L. (2019). Dirty data: Content moderation, regulatory
outsourcing, and the cleaners. \emph{Film Quarterly}, \emph{73}(1),
11--18.

@@

\leavevmode\hypertarget{ref-sorrentino2019epidemiology}{}%
Sorrentino, A., Baldry, A. C., Farrington, D. P., \& Blaya, C. (2019).
Epidemiology of cyberbullying across europe: Differences between
countries and genders. \emph{Educational Sciences: Theory \& Practice},
\emph{19}(2).

\leavevmode\hypertarget{ref-steiger2021psychological}{}%
Steiger, M., Bharucha, T. J., Venkatagiri, S., Riedl, M. J., \& Lease,
M. (2021). The psychological well-being of content moderators.
\emph{Proceedings of the 2021 CHI Conference on Human Factors in
Computing Systems, CHI}, \emph{21}.

\leavevmode\hypertarget{ref-steinhardt2017certified}{}%
Steinhardt, J., Koh, P. W., \& Liang, P. (2017). Certified defenses for
data poisoning attacks. \emph{Proceedings of the 31st International
Conference on Neural Information Processing Systems}, 3520--3532.

\leavevmode\hypertarget{ref-steinhardt2015learning}{}%
Steinhardt, J., \& Liang, P. (2015). Learning fast-mixing models for
structured prediction. \emph{International Conference on Machine
Learning}, 1063--1072. PMLR.

\leavevmode\hypertarget{ref-stepanikova2012racial}{}%
Stepanikova, I. (2012). Racial-ethnic biases, time pressure, and medical
decisions. \emph{Journal of Health and Social Behavior}, \emph{53}(3),
329--343.

@@

\leavevmode\hypertarget{ref-vogels_state_2021}{}%
Vogels, E. A. (2021). The {State} of {Online} {Harassment}. Retrieved
from
\url{https://www.pewresearch.org/internet/2021/01/13/the-state-of-online-harassment/}
